Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-25 paper/paper.Rmd
rewrite standalone implementation vs ecosystem

<!-- FIXME: mention missing spatiotemporal buffering method -->

<!-- missing: non-LOO method with buffer support -->
<!-- FIXME: this is wrong, leave-one-disc-out does this -->
Also no methods yet exists that makes use of a buffer zone with blocking or clustering, bridging the gap between buffered LOO-CV and fold-based non-buffer methods (`"spcv_coords"` and `"spcv_block"`).

We believe that making resampling methods available to widely used modeling frameworks is more beneficial than implementing such methods standalone in an R package.
The latter often require special structured objects as inputs and cannot directly be re-used in subsequent modeling steps of user workflows.
This is not an issue specific to spatiotemporal resampling methods but a general philosophy of the authors.

Spatiotemporal cross-validation is still not yet a paradigm that is completely established in scientific workflows even though it is discussed intensively for more than a decade now.
Making most available methods easily accessible to users is an important step to foster the acceptance of such in the community and lead to less biased cross-validation results in environmental and ecological studies.

>>>>

<!--mention missing spatiotemporal buffering method -->
As of writing this paper, there is no buffering methods which operates in the spatiotemporal domain.

<!-- mention pros and cons of implementing methods in a standalone pkg vs a framework -->
There are pros and cons on whether a new method should be integrated into an existing ecosystem such as \pkg{mlr3} directly first or distributed via a standalone package.
On the upside, developers can benefit from existing package structures and orient themselves how previous methods were implemented.
Also, the new method will be directly usable by all people using this ecosystem following an existing and familiar syntax.
Contributors do not have to commit maintaining the package in the future, possibly risking its removal in case of major issues.
In addition, they most likely get a thorough review from other community members during the implementation, possibly enhancing the code side of the implementation.
On the contrary, people are forced to use the ecosystem and cannot easily use the method outside of it, whether its a different ecosystem or some other way.
They might also be forced to follow certain guidelines of the ecosystem and potentially feel constrained in their way of doing things.

<!-- signoff -->
Spatiotemporal cross-validation is still not yet a paradigm that is completely established in scientific workflows even though it is discussed intensively for more than a decade now.
Making most available methods easily accessible to users is an important step to foster the acceptance of such in the community and lead to less biased cross-validation results in environmental and ecological studies.
